### 2014-06-01 writing/S'14 paper/intro.tex
Quantifier section update. Not done yet.

Deep learning methods in NLP which learn vector representations for words have seen successful uses in recent years on increasingly sophisticated tasks \cite{collobert2011natural, socher2011semi, socher2013acl1, chen2013learning}. Given the still modest performance of semantically rich NLP systems in many domains---question answering and machine translation, for instance---it is worth exploring the degree to which learned vectors can serve as general purpose semantic representations. 
Much of the work to date analyzing vector representations for words (see \cite{baroni2013frege}) has focused on lexical semantic behaviors---like the similarity between words like \ii{Paris} and \ii{France}. Good similarity functions are valuable for many NLP tasks, but there are real use cases for which it is necessary to know how words relate to one another or to some extrinsic representation, and to model the ways in which word meanings combine to form phrase, sentence, or document meanings. This paper explores the ability of linguistic representations developed using supervised deep learning techniques to support interpretation and reasoning.

@@

There are two broad family of tasks that could be used to test the ability of a model to develop general purpose meaning representations. In an interpretation task, sentences are mapped onto some denotation, such as  \ii{true} or \ii{false} for statements, or a factual answer for questions. There has been preliminary work in developing distributed models for interpretation \cite{grefenstette2013towards, rocktaschellow}, but developing a representation of world knowledge that corresponds accurately to the content expressed in language introduces considerable design challenges. I approach the problem by way of an inference task instead. Inferring the truth of one sentence from another does not require any preexisting knowledge representations, but nonetheless requires a precise representation of sentence meaning. I borrow the structure of the task from MacCartney and Manning  \cite{maccartney2009extended}. In it, the model is presented with a pair of sentences, and made to label the logical relation between the sentences as equivalence, entailment, or any of five other classes, as here:

\begin{quote}
\begin{enumerate}\small
\item Many smartphone users avoid high bills overseas by disabling data service.
\item Not everyone uses their smartphones for email when traveling abroad.
\end{enumerate} 
$\Rightarrow$ Entailment
\end{quote}

In this paper, we test the ability of recursive models to on three simple tasks, each of which is meant to capture a property that is necessary in representing natural language meaning in the setting of inference. I begin with an overview of MacCartney and Manning's \cite{maccartney2009extended} framework for inference, and of the recursive neural networks that I study. by showing that these models can learn to correctly represent entailment representations between sentences. I then show that these models can capture the meanings of recursive structurers accurately up to a sufficient depth. I finally close with a brief demonstration of the ability of these models to reason over short natural language sentences involving quantifiers.

>>>>

% Deep learning methods in NLP which learn vector representations for words have seen successful uses in recent years on increasingly sophisticated tasks \cite{collobert2011natural, socher2011semi, socher2013acl1, chen2013learning}. Given the still modest performance of semantically rich NLP systems in many domains---question answering and machine translation, for instance---it is worth exploring the degree to which learned vectors can serve as general purpose semantic representations. Much of the work to date analyzing vector representations for words (see \cite{baroni2013frege}) has focused on lexical semantic behaviors---like the similarity between words like \ii{Paris} and \ii{France}. Good similarity functions are valuable for many NLP tasks, but there are real use cases for which it is necessary to know how words relate to one another or to some extrinsic representation, and to model the ways in which word meanings combine to form phrase, sentence, or document meanings. This paper explores the ability of linguistic representations developed using supervised deep learning techniques to support interpretation and reasoning.

@@

% There are two broad family of tasks that could be used to test the ability of a model to develop general purpose meaning representations. In an interpretation task, sentences are mapped onto some denotation, such as  \ii{true} or \ii{false} for statements, or a factual answer for questions. There has been preliminary work in developing distributed models for interpretation \cite{grefenstette2013towards, rocktaschellow}, but developing a representation of world knowledge that corresponds accurately to the content expressed in language introduces considerable design challenges. I approach the problem by way of an inference task instead. Inferring the truth of one sentence from another does not require any preexisting knowledge representations, but nonetheless requires a precise representation of sentence meaning. I borrow the structure of the task from MacCartney and Manning  \cite{maccartney2009extended}. In it, the model is presented with a pair of sentences, and made to label the logical relation between the sentences as equivalence, entailment, or any of five other classes, as here:

%\begin{quote}
%\begin{enumerate}\small
%\item Many smartphone users avoid high bills overseas by disabling data service.
%\item Not everyone uses their smartphones for email when traveling abroad.
%\end{enumerate} 
%$\Rightarrow$ Entailment
%\end{quote}

%In this paper, we test the ability of recursive models to on three simple tasks, each of which is meant to capture a property that is necessary in representing natural language meaning in the setting of inference. I begin with an overview of MacCartney and Manning's \cite{maccartney2009extended} framework for inference, and of the recursive neural networks that I study. by showing that these models can learn to correctly represent entailment representations between sentences. I then show that these models can capture the meanings of recursive structurers accurately up to a sufficient depth. I finally close with a brief demonstration of the ability of these models to reason over short natural language sentences involving quantifiers.

### 2014-06-01 writing/S'14 paper/quantifiers.tex
Quantifier section update. Not done yet.

% Condense condense condense

Interest in NLI in the NLP community is ongoing, and a version of it has been included in the 2014 SemEval challenge specially targeted towards the evaluation of distributional models. Neither this dataset, nor any other existing RTE and NLI datasets are appropriate for the task at hand however. I intend for the present experiment to evaluate the ability of a class of models to learn certain types of inference behavior, and need a dataset that precisely tests these phenomena. With existing datasets that use unrestricted natural language, there is the risk that a model could successfully capture monotonicity inference, but fail to accurately label test data due to problems with, for example, lexical ambiguity, syntactic ambiguity, coreference resolution, or pragmatic enrichment.

@@

The dataset is built on a small purpose-built vocabulary, which is intended to be large and diverse enough to permit a wide variety of experiments on different semantic phenomena beyond those shown here, but which is still small enough to allow the relations between the lexical items themselves to be exhaustively manually labeled when needed. The vocabulary contains 41 predicates (nouns, adjectives, and intransitive verbs; see Appendix B for more on the design of the wordlist), six quantifiers, the logical conjunctions \emph{and} and \emph{or}, and the unary operator \emph{not}.

The data take the form of 12k pairs of short sentences, each annotated with a relation label, which I divide into about 200 smaller datasets. These datasets contain tightly constrained variants of a specific valid reasoning pattern, each differing in at most one lexical item, and all sharing the same relation label. The remainder of this section describes the composition of these 200 datasets. Examples from four of the datasets are provided in Table \ref{examplesofdata}.

\begin{table}\small\centering
\begin{tabular}{|l|}
\hline
(most warthogs) walk $\natneg$ (not-most warthogs) walk\\
(most mammals) move \# (not-most (not turtles)) move\\
(most (not pets)) (not swim) $\sqsupset$ (not-most (not pets)) move\\
\hline
(no turtles) (not growl) $\|$ (no turtles) (not swim)\\
(no warthogs) swim $\sqsupset$ (no warthogs) move\\
(no warthogs) move $\sqsubset$ (no (not reptiles)) swim\\
\hline
\end{tabular}
\caption{Sample data from two different quantifier pairs.\label{examplesofdata}}
\end{table}

@@

% TODO: Condense the below to a paragraph

\noindent\textit{Basic monotonicity:} This set of datasets contains reasoning patterns like those seen in example 1  in Table \ref{examplesofdata}, where one of the predicates on one side entails the predicate in the corresponding position on the other side. In some of the datasets (as in 1), this alternation is in the first argument position, in some the second argument position, and in some both. For the alternating first argument subclasses, I have every lexical entailment pair in the data in the first argument position, the terms \ii{bark}, \ii{mobile}, and \ii{European} in the second argument position, and every quantifier. 
For alternating second argument datasets, I have all predicates in the first argument position, and the pairs \ii{bark--animate}, \ii{French--European}, and \ii{Parisian--French} in the second argument position. The datasets in which there is an alternation in both positions fall into two categories. In some, the entailment relations between the arguments work in the same direction (\ii{some dog French} $\sqsubset$ \ii{some animal European}), in others, they work in opposite directions (\ii{some dog European} \# \ii{some animal French}).

\noindent\textit{Quantifier substitution:} These datasets, exemplified in 2 above, show the interactions between each possible pair of different quantifiers, with the same predicates on both sides. Datasets exist with \ii{bark}, \ii{mobile}, and \ii{European} in the second argument position, and within each dataset every possible predicate is shown in first argument position.

\noindent\textit{Monotonicity with quantifier substitution:} These datasets show the more complex monotonicity interactions that emerge when reasoning between phrases with differing arguments and differing quantifiers, as in  3. 
Exhaustively creating datasets of this kind involves too large an amount of data to readily verify manually, so I sampled  from the extensive set of possible combinations of the six quantifiers and the fixed argument fillers used in the monotonicity datasets. Each possible relation but `$\equiv$' (which does not apply sentences like these unless the predicates on both sides are identical) is expressed, as is every possible pair of quantifiers.

\noindent\textit{Negation:}
To show the interaction of negation and monotonicity, I included variants of many of the datasets described above in which one of the four argument positions is systematically negated, as demonstrated in example 4.

@@

\begin{table}\small\centering
\begin{tabular}{|l|l|}\hline
\textbf{Training configuration} & \textbf{Test accuracy}\\\hline
\textsc{all split}	&	TODO\% \\\hline
\textsc{pair no/no}	&	TODO\% \\
\textsc{pair two/$<$two}	&	TODO\% \\
\textsc{pair not-all/not-most}	&	TODO\% \\
\textsc{pair all/some}	&	TODO\% \\\hline
\end{tabular}

>>>>

% Introduce the task

@@

Our data consists of pairs of sentences generated from a small artificial grammar. Each sentence contains a quantifier, a noun, which may be negated, and an intransitive verb which may be negated. We use the basic quantifiers \ii{some}, \ii{most}, \ii{all}, \ii{two}, and \ii{three}, and each of their duals over negation \ii{no}, \ii{not-all}, \ii{not-most}, \ii{less-than-two}, and \ii{less-than-three}. We also include five nouns, four intransitive verbs, and the negation symbol \ii{not}. In order to be able to define relations between sentences with differing lexical items, we define the lexical relations between each noun--noun pair, each verb--verb pair, and each quantifier--quantifier pair.

%nouns = ['warthogs', 'turtles', 'mammals', 'reptiles', 'pets']
%verbs = ['walk', 'move', 'swim', 'growl']
%dets = ['all', 'not_all', 'some', 'no', 'most', 'not_most', 'two', 'lt_two', 'three', 'lt_three']
%adverbs = ['', 'not']

To assign relation labels to sentence pairs, we built a small task-specific implemenation of MacCartney's logic that can accurately label sentences of this restricted language. The logic is not able to derive all intuitively true relations of this language, and fails to derive a single unique relation for certain types of statement, including De Morgean's laws (e.g. \ii{(all pets) growl $\natneg$ (some pet) (not growl)}), and we simply discard these examples. Exhaustively generating the valid sentences under this grammar and choosing those to which a relation label can be assigned
yields 66k sentence pairs. Some examples of these data are provided in Table \ref{examplesofdata}.

\begin{table}\small\centering
\begin{tabular}{|l|}
\hline
\ii{(most warthogs) walk $\natneg$ (not-most warthogs) walk}\\
\ii{(most mammals) move $\#$ (not-most (not turtles)) move}\\
\ii{(most (not pets)) (not swim) $\sqsupset$ (not-most (not pets)) move}\\
\hline
\ii{(no turtles) (not growl) $\|$ (no turtles) (not swim)}\\
\ii{(no warthogs) swim $\sqsupset$ (no warthogs) move}\\
\ii{(no warthogs) move $\sqsubset$ (no (not reptiles)) swim}\\
\hline
\end{tabular}
\caption{Sample data involving two different quantifier pairs.\label{examplesofdata}}
\end{table}

@@

@@

\begin{table}\small\centering
\begin{tabular}{|l|l|}\hline
\textbf{Training configuration} & \textbf{Test accuracy}\\\hline
\textsc{all split}	&	TODO\% \\\hline
\textsc{pair no/no}	&	TODO\% \\
\textsc{pair two/less-than-two}	&	TODO\% \\
\textsc{pair not-all/not-most}	&	TODO\% \\
\textsc{pair all/some}	&	TODO\% \\\hline
\end{tabular}
